---
title: "Using Opsum Toolbox"
author: "Jonathan Harris"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## opsumToolbox User Guide

OpsumToolbox version 0.1 provides a utility for extracting data from U.S. Coast Guard cutter operational summaries and transforming it into a dataframe for further analysis. To run the development version of this software, you will need to have the `devtools` package installed. Then you can run the command:
  
```{r, echo=TRUE, eval=FALSE}
devtools::install_github("jrh05/opsumToolbox")
```

This command will install the latest stable version of the package from github, and it will also install the package dependencies `plyr` and `dplyr` if they are not already installed. The example below utilizes the `readtext` and `quanteda` packages.

```{r }
library(readtext)
library(quanteda)
library(opsumToolbox)

opsum.dir <- system.file("extdata", package = "opsumToolbox")
OPSUMS <- readtext(opsum.dir)
corpus_txt <- corpus(OPSUMS)
docnames(corpus_txt) <- OPSUMS$doc_id
x <- texts(corpus_txt)
y <- cgOpsum(x)
z <- data.frame.cgOpsum.list(y)
z$DTG.START <- DTG(z$`PERIOD COVERED.START`)
z$POSIXUTC.START <- as.POSIXct(z$DTG.START, tz = "GMT")
z <- z[order(z$POSIXUTC.START), ]
z[, c("PERIOD COVERED.START", "CO COMMENTS")]
z[, c("MSG DTG", "PERIOD COVERED.START", "DTG.START", "POSIXUTC.START")]
y.feb <- subset(y, grep("FEB", x, ignore.case = TRUE))
```
