---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## opsumToolbox User Guide

OpsumToolbox version 0.1 provides a utility for extracting data from U.S. Coast Guard cutter operational summaries and transforming it into a dataframe for further analysis. To run the development version of this software, you will need to have the "devtools" package installed. Then you can run the command:
  
  ```{r, echo=TRUE, eval=FALSE}
devtools::install_github("jrh05/opsumToolbox")
```

This command will install the latest stable version of the package from github, and it will also install the package dependencies "plyr" and "dplyr" if they are not already installed.

```{r }
library(readtext)
library(quanteda)
library(opsumToolbox)

opsum.dir <- "~/My_Documents/CGA/capshare/capshare/OPSUM"
OPSUMS <- readtext(opsum.dir)
corpus_txt <- corpus(OPSUMS)
docnames(corpus_txt) <- OPSUMS$doc_id
x <- texts(corpus_txt)
y <- cgOpsum(x)
z <- data.frame.cgOpsum.list(y)
names(z)
y.dive <- subset(y, grep("dive", x, ignore.case = TRUE))
```

Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
